---
title       : Course Project - Developing Data Products
subtitle    : 
author      : Lee Murray
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Historical Weather Event Data Visualization

This presentation is about the exciting new Historical Weather Event Data Visualization app
Using the massive power of R and shiny, you can now find out how much damage past weather
events caused on a state by state basis.


--- 

## DETAILS!

The app works as follows: Select a date range and a state and whether you want to see
economic or population damages and the app will display a barplot of the weather categories
contributing to the top 80% of the relevant damages. AMAZING!

You can go play with it right now at [WeatherView](https://lemurey.shinyapps.io/WeatherView/)

---

## Slide 4 (it's better than Slide 3)
This app was based on the NOAA database used for the reproducible research course.
I applied some transformations to the data that you can read about [on my github page](https://github.com/lemurey/datascience-shiny-app)
  
A brief summary- I filtered out everything before 1991, then applied an
inflation adjustment to the monetary values. I then grab the event 
categories that correspond to the top 80% of any given damage type.

The original data can be found [here.](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2)

---

## data.table is great

The app uses the powerful data.table R package to perform calculations, it's great.

I used calculations like these, and some regular expressions to combine
similar categories and make the graphs easier to follow.

```{r echo=FALSE}
library(data.table)
load('../forap.rda')
```
```{r example data.table}
twt[year %in% c('1991','1992','1993'),.(sum(FATALITIES)),by=STATE]

head(twt)
```
